### 2016-09-27 intro.tex
notes from phone call
cheers
no message
First pass at intro, some cleanup in Section 2

\section{Introduction}
\label{sec:intro}
\tsnote{Skeleton text from old intro.  (Full version of old intro now
  in an appendix.} \jnote{Too focused on Bloom filters for my
  taste.}
We revisit the formalization of Bloom filters~\cite{xxx} and closely
related data structures as primitives with explicit security goals.
Recently, Naor and Yogev~\cite{xxx} (hereafter NY) gave such a
formalization, providing syntax for a generalized abstraction of
Bloom filters, as well as casting the classical Bloom filter
soundness condition as a security experiment admitting adaptive
adversaries.  To briefly summarize, a Bloom filter is a data
structure for compactly representing a set~$\mathcal{S}$ in a way
that supports constant-time responses to set-membership queries. The
representation of~$\mathcal{S}$ is a bit-array~$M$ of length~$m$,
all initially set to~0.  To insert $x \in \mathcal{S}$ into~$M$, one
computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i
\colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a
universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices
of~$M$.  The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set
to 1; if a bit is already 1, due to inserting some previous element
of~$\mathcal{S}$, then it is left alone.  After all elements
of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is
taken as the representation.  To test if $y \in \mathcal{S}$, one
checks if
\[
(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1),
\]
returning ``yes'' if so, and ``no'' otherwise. Bloom
filters are correct, in the sense that if $y \in \mathcal{S}$, the
set-membership test always returns ``yes''.  The classical soundness
condition asserts that for all $\mathcal{S}$ and any $y
\notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr
\mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots
\wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the
false-positive error, is a parameter of the Bloom filter.  (The
values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
well-known way.) NY recast this soundness condition as a game in
which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
set-membership queries, and it attempts to find one or more false
positives. The fact that~$A$ can \emph{adapt} its queries and its
output based on what it learns from the set-membership oracle (but,
as we will see, not upon the hash functions) is the key definitional
contribution of~NY.

Bloom filters have a broad range of practical applications, for
example, in content-distribution networks, large database query
processing, routing algorithms for peer-to-peer networks, protocols
for establishing linkages between medical-record databases, fair
routing of TCP packets, Bitcoin wallet synchonization. \tsnote{need
  citations}

\heading{Our contributions. }
Given these shortcomings and the prevalent use of Bloom filters in practice, we revisit the matter of formalizing them as primitives with explicit security goals, these goals being abstracted from the attack surface they expose in practice.   We begin by giving a new syntax for hash-based filters, which more clearly captures Bloom filters...

We generalize this syntax to hash-based filters that are mutable,
%\jnote{I find ``mutable'' a slightly awkward term, maybe because it makes me think of mutability in the context of programming languages. In much data structures literature, this is called the ``dynamic'' case, in contrast to the ``static'' case.}
%
%\tsnote{I adopted this term after reading it in some bloom filter paper(s). Ironically, I liked it for the same reason you think it is awkward :) My PL association to the term is that an immutable object is one whose state cannot be modified after it is created, and a mutable object is the opposite.  But I don't really care too much.}
in the sense
that they allow for updating of the representation. This allows us
to capture counting Bloom filters, spectral Bloom filters, stable
Bloom filters, count-min sketches, and other compact set
representation data structures...

We provide various security notions for these primitives... FP with private, public representation coins; set privacy with private, public representation coins; FP/set privacy in the multi-representation setting (outsider attack, think CDNs); FP/set privacy in the multi-representation setting with corruptions (insider attack, think P2P networks) \tsnote{Those are just the ones that come to mind now.  Could also consider authenicity of representations, think CDN or P2P settings.}

We show that...

\heading{Related work: attacks}
\begin{itemize}
\item Niedermayer et al., ``Cryptanalysis of Basic Bloom Filters Used for Privacy-Preserving Record Linkage'', breaking privacy of secret-hash-function Bloom filters. \tsnote{Journal of Privacy and Confidentiality, 2014}
\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{DSN'15: Looks like a real goldmine of related work!}
\item Crosby and Wallach, ``Denial of Service via Algorithmic Complexity Attacks'' \tsnote{Gives attacks on Squid}
\item Gao et al., ``Internet Cache Pollution Attacks and Countermeasures''
\end{itemize}

\heading{Related work: definitions(?)}
\begin{itemize}
\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''. \tsnote{Gives some security definitions for privacy. Quick scan, not super clear what they achieve. The definition of client-privacy (Definition 1) for example, makes no sense to me.  Actually, likewise for server-privacy (Definition 2).  Both seem vague and thoroughly underspecified.}
\item Naor and Yogev
\item Eujin Goh, ``Secure Indexes'' \tsnote{A secure index can
    be used for set membership.  Builds a secret-key data
    structure (an Index) that allows searching for keyword~$w$
    if one holds the trapdoor $T_w$ for~$w$, where the trapdoor
    depends on the secret key.  Main construction uses
    traditional Bloom filters and a PRF.  Construction appears
    quite inefficient, needing a very long secret key, turning a
    keyword~$w$ into a bunch of PRF outputs, and then storing
    each of these PRF outputs in the BF.  Havent read the full
    analysis; don't know if this was ever published. }
    \jnote{Never published. I think this work uses Bloom filters
    for encrypted search; I don't remember the paper having much
    to say about Bloom filters themselves.}
\end{itemize}

@@

\heading{Related work: tangential}
\begin{itemize}
\item Chang and Mitzenmacher ``Privacy Preserving Keyword Searches on Remote Encrypted Data''.
\item Mitzenmacher and Vadhan. ``Why Simple Hash Functions Work: Exploiting the Entropy in a Data Stream''.
\item Dodis et al. ``Fuzzy Extractors: How to Generate Strong Keys from Biometrics and Other Noisy Data'' \tsnote{Introduces ``secure sketches'', which is a representation of a single-element set that is information theoretically private (up to some function of the min-entropy of the element); only tangentially related to ``sketches'' as defined in the Bloom filter literature.}
\end{itemize}

>>>>

\section{Introduction}
\label{sec:intro}

Data structures are a fundamental tool used throughout computer
science. Typically, when the behavior of a data structure (e.g., its
running time or its error probability) is analyzed, the analysis is
performed under the assumption that the input/queries to the data
structure are chosen independently of the data structure itself, and
in particular independent of any internal randomness used by the
data structure. But, as recently highlighted by Naor and
Yogev~\cite{naor2015bloom}, there are many natural scenarios in
which the input/queries may be chosen \emph{adversarially} and
\emph{adaptively} based on partial information and/or prior
observations about the data structure.

In addition, standard applications of data structures assume that
the party querying the data structure is fully trusted, and hence
privacy concerns do not arise. In some scenarios, however, it may be
desirable to allow some party to pose (certain types of) queries to
a data structure, but unacceptable to leak the data in its entirety
to that same party. Existing definitions do not address this at~all.

The concerns outlined above motivate a careful treatment of data
structures in an adversarial setting, where both \emph{soundness}
\jnote{I like soundness better than correctness, but I won't
insist.} and \emph{correctness} are considered. In this work we
initiate such a treatment for abstract data structures, and also
explore the security of several specific data structures---that can
all be viewed as generalizations of Bloom
filters~\cite{bloom1970space}---supporting (approximate)
set-membership queries. Specifically, we show \ldots

\heading{Comparison to~\cite{naor2015bloom}.} Naor and
Yogev~\cite{naor2015bloom} recently considered the problem of
adversarial soundness for (variants of) Bloom filters and, indeed,
their worked served as inspiration for our own. Our work extends
their work significantly in several directions. For starters, we
consider abstract data structures (rather than only the case of
set-membership data structures), and consider privacy in addition to
soundness. Even with respect to the specific case of soundness for
set-membership data structures, our work offers several advantages
to the Naor-Yogev treatment:
\begin{itemize}
\item We explicitly distinguish between public and private
    portions of a data structure, something that was left
    ambiguous in~\cite{naor2015bloom}. This allows us, for
    example, to distinguish between the hash-function keys and
    the bit array when discussing classical Bloom filters.
\item The Naor-Yogev definition of soundness allows the
    adversary to make several set-membership queries, some of
    which may produce incorrect results, and the attacker then
    succeeds if it can output a \emph{fresh} query which leads
    to an error. We propose instead what we find to be a more
    natural definition in which the attacker succeeds if it can
    cause a certain number of incorrect results.
\item Naor and Yogev analyze a new Bloom-filter construction of
    their own design. In contrast, we are interested in
    analyzing practical constructions that have been proposed in
    prior work to understand how secure they are. In particular,
    we analyze Bloom filters in the random-oracle model.
    \jnote{Do we? Perhaps we want to explicitly adapt some of
    our definitions to the ROM?}
\end{itemize}

%false-positive error, is a parameter of the Bloom filter.  (The
%values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
%well-known way.) NY recast this soundness condition as a game in
%which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
%set-membership queries, and it attempts to find one or more false
%positives. The fact that~$A$ can \emph{adapt} its queries and its
%output based on what it learns from the set-membership oracle (but,
%as we will see, not upon the hash functions) is the key definitional
%contribution of~NY.

%Bloom filters have a broad range of practical applications, for
%example, in content-distribution networks, large database query
%processing, routing algorithms for peer-to-peer networks, protocols
%for establishing linkages between medical-record databases, fair
%routing of TCP packets, Bitcoin wallet synchonization~\cite{schnell2011novel,niedermeyer2014cryptanalysis,gervais2014privacy,nojima2009cryptographically,feng2001stochastic,reynolds2003efficient,byers2002informed,broder2004network}.

\ignore{We provide various security notions for these primitives...
FP with private, public representation coins; set privacy with
private, public representation coins; FP/set privacy in the
multi-representation setting (outsider attack, think CDNs); FP/set
privacy in the multi-representation setting with corruptions
(insider attack, think P2P networks) \tsnote{Those are just the ones
that come to mind now.  Could also consider authenticity of
representations, think CDN or P2P settings.}}

\heading{Related work.} \jnote{See the discussion of related work in
Naor-Yogev. We should cite [LN93]. I can't tell how relevant [MNS11]
is. [HW13] seems relevant, though I don't think it is captured by
our current definitions.}

\jnote{Discuss use of BFs and BF variants in a security-oriented
setting. Also some prior work formalizing BFs in an adversarial
environment. See commented out portion of the .tex}

\ignore{\heading{Related work: attacks}
\begin{itemize}
\item Niedermayer et al., ``Cryptanalysis of Basic Bloom Filters Used for Privacy-Preserving Record Linkage'', breaking privacy of secret-hash-function Bloom filters. \tsnote{Journal of Privacy and Confidentiality, 2014}
\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.
\tsnote{DSN'15: Looks like a real goldmine of related work!}
\item Crosby and Wallach, ``Denial of Service via Algorithmic Complexity Attacks'' \tsnote{Gives attacks on Squid}
\item Gao et al., ``Internet Cache Pollution Attacks and Countermeasures''
\end{itemize}}

\ignore{\heading{Related work: definitions(?)}
\begin{itemize}
\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''.
\tsnote{Gives some security definitions for privacy. Quick scan, not super
clear what they achieve. The definition of client-privacy
 (Definition 1) for example, makes no sense to me.  Actually,
 likewise for server-privacy (Definition 2).  Both seem vague
 and thoroughly underspecified.}
\item Naor and Yogev
\item Eujin Goh, ``Secure Indexes'' \tsnote{A secure index can
    be used for set membership.  Builds a secret-key data
    structure (an Index) that allows searching for keyword~$w$
    if one holds the trapdoor $T_w$ for~$w$, where the trapdoor
    depends on the secret key.  Main construction uses
    traditional Bloom filters and a PRF.  Construction appears
    quite inefficient, needing a very long secret key, turning a
    keyword~$w$ into a bunch of PRF outputs, and then storing
    each of these PRF outputs in the BF.  Havent read the full
    analysis; don't know if this was ever published. }
    \jnote{Never published. I think this work uses Bloom filters
    for encrypted search; I don't remember the paper having much
    to say about Bloom filters themselves.}
\end{itemize}

@@

\heading{Related work: tangential}
\begin{itemize}
\item Chang and Mitzenmacher ``Privacy Preserving Keyword Searches on Remote Encrypted Data''.
\item Mitzenmacher and Vadhan. ``Why Simple Hash Functions Work: Exploiting the Entropy in a Data Stream''.
\item Dodis et al. ``Fuzzy Extractors: How to Generate Strong Keys from Biometrics and Other Noisy Data'' \tsnote{Introduces ``secure sketches'', which is a representation of a single-element set that is information theoretically private (up to some function of the min-entropy of the element); only tangentially related to ``sketches'' as defined in the Bloom filter literature.}
\end{itemize}
}

### 2016-09-27 ny-def-comparison.tex
First pass at intro, some cleanup in Section 2

\jnote{Just noticed something (else) odd about the NY definition: we cannot assume w.l.o.g.\
that $A$ makes exactly $q$ queries, and in fact it is possible to have cases where increasing
the number of queries the attacker makes can decrease its advantage! This seems like
another drawback of the definition.}\tsnote{Really?  That seems worth
pointing out, as part of our list of complaints.}

>>>>

%\jnote{Just noticed something (else) odd about the NY definition: we cannot assume w.l.o.g.\
%that $A$ makes exactly $q$ queries, and in fact it is possible to have cases where increasing
%the number of queries the attacker makes can decrease its advantage! This seems like
%another drawback of the definition.}\tsnote{Really?  That seems worth
%pointing out, as part of our list of complaints.}

### 2016-09-27 syntax.tex
notes
my changes to syntax
First pass at intro, some cleanup in Section 2

\newcommand{\qry}{\mathsf{qry}}
\section{(Multiset) Data Structures}

\heading{Preliminaries. } When~$\univ$ is a set and $n>0$ is an
integer, we let $[\univ]^n$ denote the set of all size-$n$ subsets
of~$\univ$, and $[[\univ]]^n$ for the set of all multisets
over~$\univ$ with total multiplicity~$n$. \jnote{I guess we are
viewing sets as a special case of multisets, so maybe just say
that.}  We write $x \getsr \univ$ to denote
sampling an element uniformly from~$\univ$ and assigning it to~$x$,
and we extend this notation to randomized algorithms. When~$X$ is a
string over some alphabet~$\Sigma$, we write $|X|$ for the bitlength
of~$X$, relative to some fixed encoding.  When~$X$ is a multiset, we
overload the notation so that~$|X|$ is the total multiplicity
of~$X$.

Algorithms may be provided black-box access to one or more oracles,
which we write as superscripts, e.g., $F^{O_1,O_2,\ldots}$.  An \emph{adversary} is a randomized algorithm.

\heading{Data structures.}  We begin by defining a general primitive
that produces a representation of a given multiset, and provides a
mechanism to answer a specified collection of questions about that
multiset.
%Informally, the representation should serve as a good
%approximation of the multiset, at least with respect to the allowed queries.
\begin{definition}[Data structure] \rm
Fix a non-empty set~$\univ$, and a collection of (multi)sets~$\calS$
over $\univ$. A \emph{data structure} (for $\calS$) is a tuple
$\setprim=(\calQ,\Rep, \Qry)$ where:
\begin{itemize}
\item $\mathcal{Q}=\{\qry \colon \mathcal{S} \to \Gamma\}$ is a set
    of supported \emph{queries}, where $\Gamma$ is the set of query \emph{answers}.
\item $\Rep \colon \mathcal{S} \to \bits^*
    \times \bits^*$ is a randomized \emph{representation
    algorithm}, taking as input a (multi)set $S \in \mathcal{S}$, and outputting %a \emph{representation} $M \in \Sigma^*$,
    \emph{public representation data} $\pubaux \in \bits^*$ and
    \emph{private representation data} $\privaux \in \bits^*$. We write
    $(\pubaux,\privaux) \getsr \Rep(S)$ as shorthand for this execution.
\item $\Qry\colon \bits^* \times \bits^* \times \calQ \to
    \Gamma$ is a deterministic \emph{query-evaluation}
    algorithm, taking as input $\pubaux,\privaux \in \bits^*$
    and a query $\qry \in \calQ$, and outputting an \emph{answer}
    $a \in \Gamma$.  We write $a \gets \Qry(\pubaux,\privaux,\qry)$
    for this execution.
\end{itemize}
\hfill\dqed
\end{definition}

@@

\begin{definition}[Error probability and rate] \rm
For a given data structure $\setprim=(\calQ,\Rep, \Qry)$, let
$\mathrm{Err}(S,\qry,\pubaux,\privaux)$ be a predicate that is true iff
$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$.  Then $\Pi$ has \emph{error
probability} $\epsilon$ if $\max_{S,\qry}\Pr[(\pubaux,\privaux) \getsr
\Rep(S) : \mathrm{Err}(S,\qry,\pubaux,\privaux)=1 ] \leq \epsilon$.
%
It has \emph{error rate} $\tilde{\epsilon}$ if
$\max_{S}\Pr[(\pubaux,\privaux) \getsr \Rep(S);\, \qry \getsr \calQ :
\mathrm{Err}(S,\qry,\pubaux,\privaux)=1] \leq \tilde{\epsilon}$. \hfill\dqed
\end{definition}

@@

Let~$\Pi$ be a data structure that has error-probability $\epsilon$,
and consider a correctness-violating attack that asks random
queries $\qry_1,\qry_2,\ldots,\qry_T$, i.e., uniform samples from~$\calQ$.
Let $\mathrm{Err}_i$ be a random variable indicating the event
$\Qry(\pubaux,\privaux,\qry_i)\neq \qry_i(S)$.  We know that the probability
that $\mathrm{Err}_i=1$ is at most~$\epsilon$, and it is tempting to
model the~$\mathrm{Err}_i$ as i.i.d. Bernoulli trials with success
probability~$\epsilon$. However, a moment's reflection shows that
this is not the case.  Concretely, consider the following scheme.
Fix $|S|=n$ for all $S \in \calS$, where $n \ll |\univ|$. For the
queries, let $\calQ = \{\qry_x\colon \calS \to \bits \,|\, \forall x
\in \univ\}$ where $\forall S \in \calS$ the predicate $\qry_x(S)=1
\Leftrightarrow x \in S$.  Let $\Rep(S)$ pick a random element~$s
\in S$, and return $M = S \setminus \{s\}$ and $\privaux =
\emptystring$.  To respond to queries,
let~$\Qry(\pubaux,\privaux,\qry_x)=1$ iff $x \in M$.  It is easy to see
that this scheme is $1/n$-correct; for any fixed~$S$, there are
exactly~$n$ queries~$\qry_x$ that have probability~$1/n$  (over the
coins of~$\Rep$) of causing a correctness error, and the remaining
$|\univ|-n$ queries have probability zero of causing an error.
Moreover, once the coins of~$\Rep$ are fixed, there is exactly
\emph{one} query that will cause an error.  Thus for random queries
from~$Q$, for all~$i\in[T]$ we have
$\Prob{\mathrm{Err}_i=1}=1/|\univ| \ll 1/n = \epsilon$.

\heading{Data structures for set-multiplicity queries.} Our
particular focus will be on data structures that support
multiplicity queries.

\begin{definition} \rm
A \emph{set-multiplicity data structure} is a data structure with
$\Gamma=\mathbb{N}$ and $\calQ=\{\qry_x\}_{x \in \univ}$, where
$\qry_x(S)$ is defined to be the multiplicity of~$x$ in the
multiset~$S$. \hfill\dqed
\end{definition}

>>>>

\newcommand{\qry}{\mathsf{qry}}
\section{Preliminaries}

When~$\univ$ is a set, we write $x \getsr \univ$ to denote sampling
an element uniformly from~$\univ$ and assigning it to~$x$. We extend
this notation to randomized algorithms, so $x \getsr A(y)$ denotes
that (randomized) algorithm $A$ is run on input~$y$, and the output
of the algorithm is assigned to~$x$. Algorithms may be provided
black-box access to one or more oracles, which we write as
superscripts, e.g., $F^{O_1,O_2,\ldots}$.

\subsection{Data Structures}

We consider an abstract notion of data structures.

%Informally, the representation should serve as a good
%approximation of the multiset, at least with respect to the allowed queries.
\begin{definition}[Data structure] \rm
Fix sets~${\cal U}, \Gamma$, and $\calQ$, where $\calQ = \{\qry
\colon {\cal U} \to \Gamma\}$. A \emph{data structure} (supporting
queries $\calQ$ over universe ${\cal U}$) is a tuple
$\setprim=(\Rep, \Qry)$ where:
\begin{itemize}
\item $\Rep \colon {\cal U} \to \bits^* \times \bits^*$ is a
    randomized \emph{representation algorithm}, taking as input
    an element $S \in \mathcal{U}$,
    and outputting %a \emph{representation} $M \in \Sigma^*$,
    \emph{public representation data} $\pubaux \in \bits^*$ and
    \emph{private representation data} $\privaux \in \bits^*$.
    We write $(\pubaux,\privaux) \getsr \Rep(S)$ as shorthand
    for this execution.
\item $\Qry\colon \bits^* \times \bits^* \times \calQ \to
    \Gamma$ is a deterministic \emph{query-evaluation}
    algorithm, taking as input $\pubaux,\privaux \in \bits^*$
    and a query $\qry \in \calQ$, and outputting an
    \emph{answer} $a \in \Gamma$.  We write $a \gets
    \Qry(\pubaux,\privaux,\qry)$ for this execution. \hfill\dqed
\end{itemize}
\end{definition}

@@

\begin{definition}[Error probability and rate] \rm
For a data structure $\setprim=(\Rep, \Qry)$ supporting queries
${\cal Q}$ over universe ${\cal U}$, let
$\mathrm{Err}(S,\qry,\pubaux,\privaux)$ be  true iff
$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$.  Then $\Pi$ has
\emph{error probability} $\epsilon$ if
$\max_{S,\qry}\Pr[(\pubaux,\privaux) \getsr \Rep(S) :
\mathrm{Err}(S,\qry,\pubaux,\privaux)=1 ] \leq \epsilon$.
%
It has \emph{error rate} $\tilde{\epsilon}$ if
$\max_{S}\Pr[(\pubaux,\privaux) \getsr \Rep(S);\, \qry \getsr \calQ :
\mathrm{Err}(S,\qry,\pubaux,\privaux)=1] \leq \tilde{\epsilon}$. \hfill\dqed
\end{definition}

@@

\jnote{The following may need to be updated to fit the new syntax.}
Let~$\Pi$ be a data structure that has error-probability $\epsilon$,
and consider a correctness-violating attack that asks random queries
$\qry_1,\qry_2,\ldots,\qry_T$, i.e., uniform samples from~$\calQ$.
Let $\mathrm{Err}_i$ be a random variable indicating the event
$\Qry(\pubaux,\privaux,\qry_i)\neq \qry_i(S)$.  We know that the
probability that $\mathrm{Err}_i=1$ is at most~$\epsilon$, and it is
tempting to model the~$\mathrm{Err}_i$ as i.i.d. Bernoulli trials
with success probability~$\epsilon$. However, a moment's reflection
shows that this is not the case. Concretely, consider the following
scheme. Fix $|S|=n$ for all $S \in \calS$, where $n \ll |\univ|$.
For the queries, let $\calQ = \{\qry_x\colon \calS \to \bits \,|\,
\forall x \in \univ\}$ where $\forall S \in \calS$ the predicate
$\qry_x(S)=1 \Leftrightarrow x \in S$.  Let $\Rep(S)$ pick a random
element~$s \in S$, and return $M = S \setminus \{s\}$ and $\privaux
= \emptystring$.  To respond to queries,
let~$\Qry(\pubaux,\privaux,\qry_x)=1$ iff $x \in M$.  It is easy to
see that this scheme is $1/n$-correct; for any fixed~$S$, there are
exactly~$n$ queries~$\qry_x$ that have probability~$1/n$ (over the
coins of~$\Rep$) of causing a correctness error, and the remaining
$|\univ|-n$ queries have probability zero of causing an error.
Moreover, once the coins of~$\Rep$ are fixed, there is exactly
\emph{one} query that will cause an error.  Thus for random queries
from~$Q$, for all~$i\in[T]$ we have
$\Prob{\mathrm{Err}_i=1}=1/|\univ| \ll 1/n = \epsilon$.

\heading{Data structures for set-membership queries.} Our particular
focus will be on data structures that support membership queries.
\jnote{I changed this from multiplicity to membership.}

\begin{definition} \rm
A \emph{set-membership data structure over $\univ$} is a data
structure with ${\cal U} \subseteq 2^\univ$, $\Gamma=\{0,1\}$, and
$\calQ=\{\qry_x\}_{x \in \univ}$, where $\qry_x(S)$ is true iff $x
\in S$. \hfill\dqed
\end{definition}

\jnote{Clean up the following, because we discuss BFs later.}
